---
title: "Prototype Report"
author: "Katie Jolly"
output: 
  html_document:
    theme: "cosmo"
    code_folding: hide
    toc: true
---

```{r include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.path = "code/example_data/output/")

options(tigris_class = "sf")
```


# Initial Mini Example

## Ramsey County: Percent White

```{r results = 'hide'}
# packages and data

library(tigris)
library(sf)
library(tidyverse)
library(randomcoloR)
library(leaflet)

# Ramsey county block groups

bg <- block_groups(state = "MN", county = "Ramsey") %>%
  st_transform(26915)

# True census tracts

tract <- tracts(state = "MN", county = "Ramsey") %>%
  st_transform(26915)

# Jolly tracts

aggregate <- st_read("code/output/prototype.shp") %>%
  st_transform(26915)

musa_4var_cv28 <- st_read("code/output/musa_4var_cv28.shp")

```


As an initial picture, there are 401 block groups in Ramsey county.

```{r}
leaflet(bg %>% st_transform(4326)) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(fillColor = "#faf7cf",
              weight = 1,
              opacity = 0.8,
              color = "#b0b5bf",
              fillOpacity = 0.6)
```


And 137 census tracts.

```{r}
leaflet(tract %>% st_transform(4326)) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(fillColor = "#e89f9b",
              weight = 1,
              opacity = 0.8,
              color = "#b0b5bf",
              fillOpacity = 0.6)
```

As an example about how to aggregate the block to groups to a larger geography to see a decrease in the margin of error I'll use `percent white` as the target variable. The spatial distribution of the total white population is mapped below.

```{r}
percent_white <- read_csv("code/example_data/white_prop_est_ramsey.csv") %>% left_join(read_csv("code/example_data/race_moe_est_ramsey.csv"))

percent_white_bg <- bg %>% left_join(percent_white %>% mutate(id = as.character(id)), by = c("GEOID" = "id"))

pal <- colorQuantile("RdPu", domain = percent_white_bg$estimate_not_hispanic_or_latino_white_alone, n = 5)

leaflet(percent_white_bg %>% st_transform(4326)) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(fillColor = ~pal(estimate_not_hispanic_or_latino_white_alone),
  weight = 1,
  opacity = 1,
  color = "white",
  fillOpacity = 0.7) %>%
  addLegend(position = "bottomright",
            pal = pal,
            values = ~estimate_not_hispanic_or_latino_white_alone,
            title = "Total white population")
```

But we know that some block groups have high margins of error. Mapped below are the coefficients of variation (cv), or the percent of the estimate covered by the margin of error. 

```{r}
percent_white_bg <- percent_white_bg %>%
  mutate(cv = if_else(estimate_not_hispanic_or_latino_white_alone == 0, NA_real_, (margin_of_error_not_hispanic_or_latino_white_alone / 1.645) / estimate_not_hispanic_or_latino_white_alone))

pal <- colorQuantile("PuBu", domain = percent_white_bg$cv, na.color = "#edf0f2", n = 5)

leaflet(percent_white_bg %>% st_transform(4326)) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(fillColor = ~pal(cv),
  weight = 1,
  opacity = 1,
  color = "white",
  fillOpacity = 0.7) %>%
  addLegend(position = "bottomright",
            pal = pal,
            values = ~cv,
            title = "Total white population coefficient of variation")
```

We can see below the most common cv is about 0.12, or 12% of the estimate for a particular block group. The general guideline is that estimates with a cv less than 0.12 are "highly reliable." Only 30% of our block groups meet that threshold. 

```{r}
#sum(percent_white_bg$cv > 0.12, na.rm = TRUE) /nrow(percent_white_bg)

ggplot(percent_white_bg, aes(x = cv)) +
  geom_histogram(fill = "#688da6", color = "white") +
  scale_x_continuous(breaks = seq(0, 1, .1)) +
  theme_minimal() +
  labs(y = "Block groups", x = "Coefficient of variation (total white population)")
```


Instead, we can aggregate the block groups to some other geography that makes sense contextually. That context changes based on the input variables. In this case we only care about contiguous block groups that look similar based on their white population. We will aggregate the block groups until each new aggregate meets some minimum cv threshold. Initially I set it to 10%, so it could go higher in later iterations.

The aggregation algorithm created 230 new geography units. Notably, that is a better resolution than the 137 census tracts. We also are guaranteed some level of homogeneity, which is not necessarily true for tracts. Below are the new aggregations with the census tract boundaries overlayed. Fill color indicates the assigned region.

```{r}
colors <- randomcoloR::distinctColorPalette(k = 230)

pal <- colorFactor(colors, domain = as.factor(aggregate$rids))

leaflet(aggregate %>% st_transform(4326)) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(fillColor = ~pal(as.character(rids)),
  weight = 1,
  opacity = 1,
  color = NA,
  fillOpacity = 0.7,
  stroke = FALSE) %>%
  addPolygons(data = tract %>% st_transform(4326),
              color = "black",
              weight = 1,
              fillColor = NA,
              fillOpacity = 0)
```

We see considerable improvement in the margins of error, but there are some that still fall above the 10% threshold so I can experiment more with other variables and thresholds. About 53% are still above the 0.12 mark, but the extremes are much closer to the desired threshold.

```{r}
aggregate_rids <- aggregate %>%
  select(-ALAND, -AWATER) %>%
  left_join(percent_white_bg %>% st_set_geometry(NULL)) %>%
  group_by(rids) %>%
  summarise(sumest = sum(estimate_not_hispanic_or_latino_white_alone),
            moeest = tidycensus::moe_sum(margin_of_error_not_hispanic_or_latino_white_alone, estimate = estimate_not_hispanic_or_latino_white_alone)) %>%
  filter(rids != -999) %>%
  mutate(cv = (moeest / 1.645)/sumest)

#sum(aggregate_rids$cv > 0.12, na.rm = TRUE) /nrow(aggregate_rids)

ggplot(aggregate_rids, aes(x = cv)) +
  geom_histogram(fill = "#688da6", color = "white") +
  scale_x_continuous(breaks = seq(0, 1, .1)) +
  theme_minimal() +
  labs(y = "Aggregates/jolly tracts", x = "Coefficient of variation (total white population)")

pal <- colorQuantile("PuBu", domain = percent_white_bg$cv, na.color = "#edf0f2", n = 5)

leaflet(aggregate_rids %>% st_transform(4326)) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(fillColor = ~pal(cv),
  weight = 1,
  opacity = 1,
  color = "white",
  fillOpacity = 0.7) %>%
  addLegend(position = "bottomright",
            pal = pal,
            values = ~cv,
            title = "Aggregated coefficient of variation")
```

# Full county example

## Seven county metro area: Percent White, Under 18, Over 65, Housing Units since 2000


```{r results = 'hide'}
# packages and data

library(tigris)
library(sf)
library(tidyverse)
library(randomcoloR)
library(leaflet)

# take out only met council region

counties_fips <- c("003", "053", "123", "163", "019", "139", "037")

# Ramsey county block groups

bg <- st_read("code/output/shp/tl_2017_27_bg.shp") %>%
  st_transform(26915) %>%
  filter(COUNTYFP %in% counties_fips)

# True census tracts

tract <- st_read("code/output/shp/tl_2017_27_tract.shp") %>%
  st_transform(26915) %>%
  filter(COUNTYFP %in% counties_fips)

# Jolly tracts

aggregate <- st_read("code/output/metc7cnty_4var.shp") %>%
  st_transform(26915)

```




As an initial picture, there are 2,085 block groups in the seven county region.

```{r}
leaflet(bg %>% st_transform(4326)) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(fillColor = "#faf7cf",
              weight = 1,
              opacity = 0.8,
              color = "#b0b5bf",
              fillOpacity = 0.6)
```


And 704 census tracts.

```{r}
leaflet(tract %>% st_transform(4326)) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(fillColor = "#e89f9b",
              weight = 1,
              opacity = 0.8,
              color = "#b0b5bf",
              fillOpacity = 0.6)
```

We want to be able to subdivide the region into some smaller geographies that are contextually meaningful.

The variables I will use are `percent white` to illustrate demographics, `over 65` and `under 18` to illustrate family structure, and `housing units built since 2000` to illustrate the housing stock. These are all going to be counted as proportions in the algorithm, rather than raw counts.

By mapping the covariates individually, we can see some patterns.

```{r}
demographics <- read_csv("code/metc_data/target/target_estimates_metc.csv") %>% left_join(read_csv("code/metc_data/target/target_moe_metc.csv"))

demographics_bg <- bg %>% left_join(demographics %>% mutate(id = as.character(id)), by = c("GEOID" = "id")) %>%
  mutate(percent_white = totalwhite/totalppl)

pal <- colorQuantile("RdPu", domain = demographics_bg$percent_white, n = 5)

leaflet(demographics_bg %>% st_transform(4326)) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(fillColor = ~pal(percent_white),
  weight = 1,
  opacity = 1,
  color = "white",
  fillOpacity = 0.7) %>%
  addLegend(position = "bottomright",
            pal = pal,
            values = ~percent_white,
            title = "Percent white population")
```


```{r}
demographics_bg$percent_over_65 <- demographics_bg$over65 / demographics_bg$total65

pal <- colorQuantile("OrRd", domain = demographics_bg$percent_over_65, n = 5)

leaflet(demographics_bg %>% st_transform(4326)) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(fillColor = ~pal(percent_over_65),
  weight = 1,
  opacity = 1,
  color = "white",
  fillOpacity = 0.7) %>%
  addLegend(position = "bottomright",
            pal = pal,
            values = ~percent_over_65,
            title = "Percent over 65 years old")
```

```{r}
demographics_bg$hu_since_2000 <- demographics_bg$built_after_2000 / demographics_bg$totalhu

pal <- colorQuantile("PuRd", domain = demographics_bg$hu_since_2000, n = 4)

leaflet(demographics_bg %>% st_transform(4326)) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(fillColor = ~pal(hu_since_2000),
  weight = 1,
  opacity = 1,
  color = "white",
  fillOpacity = 0.7) %>%
  addLegend(position = "bottomright",
            pal = pal,
            values = ~hu_since_2000,
            title = "Housing stock built since 2000")
```

The regionalization algorithm generated 167 aggregate regions. This is lower than I had expected.


```{r}
colors <- randomcoloR::distinctColorPalette(k = 230)

pal <- colorFactor(colors, domain = as.factor(aggregate$rids))

leaflet(aggregate %>% st_transform(4326)) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(fillColor = ~pal(as.character(rids)),
  weight = 1,
  opacity = 1,
  color = NA,
  fillOpacity = 0.7,
  stroke = FALSE) %>%
  addPolygons(data = tract %>% st_transform(4326),
              color = "black",
              weight = 1,
              fillColor = NA,
              fillOpacity = 0)
```



```{r}
library(tidycensus)
aggregate_rids <- aggregate %>%
  select(-ALAND, -AWATER) %>%
  left_join(demographics_bg %>% st_set_geometry(NULL)) %>%
  group_by(rids) %>%
  summarise(sumest_white = sum(totalwhite),
            sumest_pop = sum(totalppl),
            sumest_under18 = sum(under18),
            sumest_over65 = sum(over65),
            sumest_hu2000 = sum(built_after_2000),
            sumest_hu = sum(totalhu),
            moeest_white = tidycensus::moe_sum(totalwhite_moe, estimate = totalwhite),
            moeest_pop = moe_sum(totalppl_moe, estimate = totalppl),
            moeest_under18 = moe_sum(under18_moe, estimate = under18),
            moeest_over65 = moe_sum(over65_moe, estimate = over65),
            moeest_hu2000 = moe_sum(built_after_2000_moe, estimate = built_after_2000),
            moeest_hu = moe_sum(totalhu_moe, estimate = totalhu)) %>%
  filter(rids != -999) 
```

The new calculated variables show the same general distribution of values.

```{r}
ggplot(demographics_bg, aes(x = percent_over_65)) +
  geom_density(fill = "#f0e992", color = NA) +
  geom_vline(aes(xintercept = median(demographics_bg$percent_over_65, na.rm = TRUE)), color = "#4a70c2") +
  theme_minimal() +
  xlim(c(0,1)) +
  labs(title = "Block groups- percent over 65", x = "Percent over 65")

ggplot(aggregate_rids, aes(x = sumest_over65 / sumest_pop)) +
  geom_density(fill = "#f0e992", color = NA) +
  geom_vline(aes(xintercept = median(sumest_over65 / sumest_pop, na.rm = TRUE)), color = "#4a70c2") +
  theme_minimal() +
  xlim(c(0,1)) +
  labs(title = "Jolly tracts- percent over 65", x = "Percent over 65")

ggplot(demographics_bg, aes(x = percent_white)) +
  geom_density(fill = "#f0e992", color = NA) +
  geom_vline(aes(xintercept = median(percent_white, na.rm = TRUE)), color = "#4a70c2") +
  theme_minimal() +
  xlim(c(0,1)) +
  labs(title = "Block groups- percent white", x = "Percent white")

ggplot(aggregate_rids, aes(x = sumest_white / sumest_pop)) +
  geom_density(fill = "#f0e992", color = NA) +
  geom_vline(aes(xintercept = median(sumest_white / sumest_pop, na.rm = TRUE)), color = "#4a70c2") +
  theme_minimal() +
  xlim(c(0,1)) +
  labs(title = "Jolly tracts- percent white", x = "Percent white")

ggplot(demographics_bg, aes(x = hu_since_2000)) +
  geom_density(fill = "#f0e992", color = NA) +
  geom_vline(aes(xintercept = median(hu_since_2000, na.rm = TRUE)), color = "#4a70c2") +
  theme_minimal() +
  xlim(c(0,1)) +
  labs(title = "Block groups- percent of housing built since 2000", x = "Percent of housing built since 2000")

ggplot(aggregate_rids, aes(x = sumest_hu2000 / sumest_hu)) +
  geom_density(fill = "#f0e992", color = NA) +
  geom_vline(aes(xintercept = median(sumest_hu2000 / sumest_hu, na.rm = TRUE)), color = "#4a70c2") +
  theme_minimal() +
  xlim(c(0,1)) +
  labs(title = "Jolly tracts- percent of housing built since 2000", x = "Percent of housing built since 2000")
```

# MUSA study area: Percent White, Under 18, Over 65, Housing Units since 2000

After trying the method on the full seven county region, I filtered out just the study area. The algorithm took about 2 hours to run in total.

The study area has 2,001 block groups. 

```{r}
bg <- st_read("code/metc_data/target/bg_musa.shp") %>%
  st_transform(26915) 

leaflet(bg %>% st_transform(4326)) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(fillColor = "#faf7cf",
              weight = 1,
              opacity = 1,
              color = "#b0b5bf",
              fillOpacity = 1)
```

And 957 jolly tracts. This is an improvement in resolution compared to the 673 census tracts. On this map the census tract boundaries are overlayed on the Jolly tract boundaries. 

```{r}
musa_geoids <- read_csv("code/output/shp/SNC_Tracts_Incl_Cities.csv")
aggregate_musa <- musa_4var_cv28 %>%
  group_by(rids) %>%
  count()
colors <- randomcoloR::distinctColorPalette(k = 230)

pal <- colorFactor(colors, domain = as.factor(aggregate_musa$rids))

leaflet(aggregate_musa %>% st_transform(4326)) %>%
 addProviderTiles(providers$CartoDB.Positron, group = "Carto basemap") %>%
  addProviderTiles(providers$OpenStreetMap, group = "OpenStreetMap") %>%
  addPolygons(fillColor = ~pal(as.character(rids)),
  weight = 1,
  opacity =0.5,
  color = "#e9edf7",
  fillOpacity = 0.4,
  stroke = TRUE,
  highlight = highlightOptions(
    weight = 7,
    color = "#fafa70",
    bringToFront = FALSE)) %>%
  addPolylines(data = tract %>% filter(GEOID %in% musa_geoids$GEOID) %>% st_transform(4326),
              color = "black",
              weight = 1) %>%
  addLayersControl(
    baseGroups = c("Carto basemap", "OpenStreetMap"),
    options = layersControlOptions(collapsed = FALSE)
  )
```


```{r}
labels <- sprintf(
  "<strong>Block groups included: </strong>%g",
  aggregate_musa$n
) %>% lapply(htmltools::HTML)

ncolors <- colorBin("BuPu", aggregate_musa$n, bins = seq(1, 13, 2))

leaflet(aggregate_musa %>% st_transform(4326)) %>%
  addProviderTiles(providers$CartoDB.Positron, group = "Carto basemap") %>%
  addProviderTiles(providers$OpenStreetMap, group = "OpenStreetMap") %>%
  addPolygons(fillColor = ~ncolors(n),
  weight = 1,
  opacity = 1,
  color = "black",
  fillOpacity = 0.7,
  stroke = TRUE,
  highlight = highlightOptions(
    weight = 3,
    color = "#fafa70",
    bringToFront = TRUE),
  label = labels,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto"),
  group = "Jolly tracts") %>%
  addLegend(pal = ncolors, values = ~n, opacity = 1, title = "Number of block groups",
  position = "bottomright") %>%
  addLayersControl(
    baseGroups = c("Carto basemap", "OpenStreetMap"),
    overlayGroups = c("Jolly tracts"),
    options = layersControlOptions(collapsed = FALSE)
  )
```


```{r}
aggregate_rids_musa <- musa_4var_cv28 %>%
  left_join(demographics_bg %>% st_set_geometry(NULL)) %>%
  group_by(rids) %>%
  summarise(sumest_white = sum(totalwhite),
            sumest_pop = sum(totalppl),
            sumest_under18 = sum(under18),
            sumest_over65 = sum(over65),
            sumest_hu2000 = sum(built_after_2000),
            sumest_hu = sum(totalhu),
            moeest_white = moe_sum(totalwhite_moe, estimate = totalwhite),
            moeest_pop = moe_sum(totalppl_moe, estimate = totalppl),
            moeest_under18 = moe_sum(under18_moe, estimate = under18),
            moeest_over65 = moe_sum(over65_moe, estimate = over65),
            moeest_hu2000 = moe_sum(built_after_2000_moe, estimate = built_after_2000),
            moeest_hu = moe_sum(totalhu_moe, estimate = totalhu),
            propest_white = sumest_white / sumest_pop,
            propest_under18 = sumest_under18 / sumest_pop,
            propest_over65 = sumest_over65 / sumest_pop,
            propest_hu2000 = sumest_hu2000 / sumest_hu,
            moeprop_white = moe_prop(sumest_white, sumest_pop, moeest_white, moeest_pop),
            moeprop_under18 = moe_prop(sumest_under18, sumest_pop, moeest_under18, moeest_pop),
            moeprop_over65 = moe_prop(sumest_over65, sumest_pop, moeest_over65, moeest_pop),
            moeprop_hu2000 = moe_prop(sumest_hu2000, sumest_hu, moeest_hu2000, moeest_hu)) %>%
  filter(rids != -999) 
```

The variables used to aggregate have primarily moderate to high reliability. The vertical lines mark the high reliability (cv < 0.12) and moderate reliability (cv < 0.4) thresholds according to the USCB. 


```{r}
ggplot(aggregate_rids_musa, aes(x = (moeprop_white / 1.645) / propest_white)) +
  geom_density(fill = "#fa70a1", color = NA) + theme_minimal() +
  labs(x = "CV: percent white") +
  geom_vline(xintercept = 0.12) +
  geom_vline(xintercept = 0.4)

ggplot(aggregate_rids_musa, aes(x = (moeprop_under18 / 1.645) / propest_under18)) +
  geom_density(fill = "#fa70a1", color = NA) + theme_minimal() +
  labs(x = "CV: under 18 population") +
  geom_vline(xintercept = 0.12) +
  geom_vline(xintercept = 0.4)

ggplot(aggregate_rids_musa, aes(x = (moeprop_over65 / 1.645) / propest_over65)) +
  geom_density(fill = "#fa70a1", color = NA) + theme_minimal() +
  labs(x = "CV: over65 population") +
  geom_vline(xintercept = 0.12) +
  geom_vline(xintercept = 0.4)

ggplot(aggregate_rids_musa , aes(x = (moeprop_hu2000 / 1.645) / propest_hu2000)) +
  geom_density(fill = "#fa70a1", color = NA) + theme_minimal() +
  labs(x = "CV: housing built since 2000") +
  geom_vline(xintercept = 0.12) +
  geom_vline(xintercept = 0.4)
```

This is compared to the original block group margins of error.

```{r}
demographics_bg <- demographics_bg %>%
  mutate(percent_under_18 = under18 / totalppl,
         moe_percent_18 = moe_prop(under18, totalppl, under18_moe, totalppl_moe),
         moe_percent_65 = moe_prop(over65, totalppl, over65_moe, totalppl_moe),
         moe_percent_white = moe_prop(totalwhite, totalppl, totalwhite_moe, totalppl_moe),
         moe_percent_hu2000 = moe_prop(built_after_2000, totalhu, built_after_2000_moe, totalhu_moe),
         cv_percent_18 = (moe_percent_18 / 1.645)/ percent_under_18,
         cv_percent_65 = (moe_percent_65 / 1.645)/ percent_over_65,
         cv_percent_white = (moe_percent_white / 1.645) / percent_white,
         cv_percent_hu2000 = (moe_percent_hu2000 / 1.645) / (hu_since_2000 ))


ggplot(demographics_bg, aes(x = cv_percent_18)) +
  geom_density(fill = "#f0e992", color = NA) +
  geom_vline(xintercept = 0.12) +
  geom_vline(xintercept = 0.4) +
  theme_minimal() +
  labs(title = "Block groups- percent under 18", x = "CV: Percent under 18")


ggplot(demographics_bg, aes(x = cv_percent_65)) +
  geom_density(fill = "#f0e992", color = NA) +
  geom_vline(xintercept = 0.12) +
  geom_vline(xintercept = 0.4) +
  theme_minimal() +
  labs(title = "Block groups- percent over 65", x = "CV: Percent over 65")


ggplot(demographics_bg, aes(x = cv_percent_white)) +
  geom_density(fill = "#f0e992", color = NA) +
  geom_vline(xintercept = 0.12) +
  geom_vline(xintercept = 0.4) +
  theme_minimal() +
  labs(title = "Block groups- percent white", x = "CV: Percent white")


ggplot(demographics_bg, aes(x = cv_percent_hu2000)) +
  geom_density(fill = "#f0e992", color = NA) +
  geom_vline(xintercept = 0.12) +
  geom_vline(xintercept = 0.4) +
  theme_minimal() +
  labs(title = "Block groups- percent of housing built since 2000", x = "CV: Percent of housing built since 2000")

```

Based on this information, it might be beneficial to build these again not using housing built since 2000. It seems to just have fairly unreliable estimates regardless. 

On average, all of the variables show a slight decrease in CV, as expected. 

```{r}
aggregate_rids_musa_cv <- aggregate_rids_musa %>%
  mutate(cv_percent_18 = (moeprop_under18 / 1.645) / propest_under18,
         cv_percent_white = (moeprop_white / 1.645) / propest_white,
         cv_percent_hu2000 = (moeprop_hu2000 / 1.645) / propest_hu2000,
         cv_percent_65 = (moeprop_over65 / 1.645) / propest_over65) %>%
  select(contains("cv")) %>%
  st_set_geometry(NULL) %>%
  mutate(set = "Jolly tracts")

cv <- demographics_bg %>%
  select(contains("cv")) %>%
  st_set_geometry(NULL) %>%
  mutate(set = "Block group") %>%
  bind_rows(aggregate_rids_musa_cv) %>%
  gather(key = "variable", value = "cv", 1:4)

ggplot(cv, aes(x = set, y = cv)) +
  geom_boxplot(fill = "#88B7B5") +
  theme_minimal() +
  facet_wrap(~variable, scales = "free")
```

